Preliminary Experiment

### 2018-03-16 preliminary/preliminary_report.tex
another typo

Comments: It does appear that using $10$ arms instead of $3$ in this case does not appear too different. It appears that Thompson Sampling and UCB learn quickly (roughly seem to flatline at $t = 2000$) and DynamicGreedy slowly improves but does not seem to get to convergence even by $t = 10000$. However, the difference between the TS and DG trajectories is not vastly different between the 3 arm and 10 arm case. One difference to note is that it seems like one thing that does change between the two is that Dynamic $\epsilon$-greedy seems to take longer to learn (doesn't even appear to converge by $t = 10000$) in the more complex cases but seems to converge as quickly as TS and UCB in the 3 arm case.
\end{document}

>>>>

Comments: It does appear that using $20$ arms instead of $3$ in this case does not appear too different. It appears that Thompson Sampling and UCB learn quickly (roughly seem to flatline at $t = 2000$) and DynamicGreedy slowly improves but does not seem to get to convergence even by $t = 10000$. However, the difference between the TS and DG trajectories is not vastly different between the 3 arm and 20 arm case. One difference to note is that it seems like one thing that does change between the two is that Dynamic $\epsilon$-greedy seems to take longer to learn (doesn't even appear to converge by $t = 10000$) in the more complex cases but seems to converge as quickly as TS and UCB in the 3 arm case.
\end{document}
